Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-09-02 WSSSPE3/report/WSSSPE3_review.tex

After the keynote and lightning talks, the workshop facilitators led an exercise to create working
groups for the rest of the meeting.  The
attendees first suggested additional topics beyond those in the call for participation (as listed in
\S\ref{sec:preworkshop}).  One topic that was introduced at this point was ``Building Sustainable
User Communities for Scientific Software.''  The full set of topics was then placed on
flipchart-sized pieces of paper around the walls, and the attendees voted on which topics
they were strongly interested in working on at WSSSPE3, and which topics they were 
generally interested in contributing to, but not as strongly.  This led to some topics being
taken out of the mix for the rest of the workshop, since not enough people wanted to contribute
to them to lead to a useful discussion.  Additionally, some topics were brought together by the
participants who felt they were closely linked and that a group could address multiple of them
in a single discussion.

>>>>

After the keynote and lightning talks, the workshop facilitators led an exercise to create working
groups for the rest of the meeting.  The
attendees first suggested additional topics beyond those in the call for participation (as listed in
\S\ref{sec:preworkshop}).  One topic that was introduced at this point was ``Building Sustainable
User Communities for Scientific Software.''  The full set of topics was then placed on
flipchart-sized pieces of paper around the walls, and the attendees voted on which topics
they were strongly interested in working on at WSSSPE3, and which topics they were 
generally interested in contributing to, but not as strongly.  This led to some topics being
taken out of the mix for the rest of the workshop, since not enough people wanted to contribute
to them to lead to a useful discussion.  Additionally, some topics were combined by the
participants who felt they were closely linked and that a group could address multiple of them
in a single discussion.
